BOAST

### 2014-12-02 Tutorial/Tutorial-BOAST.tex
Changed open in opn
Added option to For class creation. :step is now an option.

\begin{frame}[fragile]
\frametitle{Sample Code: Procedure Declaration}
The following declaration:
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
p = Procedure("magic_filter", [n,ndat,x,y], [lowfil,upfil])
open p
\end{lstlisting}
\normalsize 
Outputs Fortran:
\tiny
\lstset{language=Fortran,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
subroutine magicfilter(n, ndat, x, y)
  integer(kind=4), parameter :: lowfil = -8
  integer(kind=4), parameter :: upfil = 7
  integer(kind=4), intent(in) :: n
  integer(kind=4), intent(in) :: ndat
  real(kind=8), intent(in), dimension(0:n-1, ndat) :: x
  real(kind=8), intent(out), dimension(ndat, 0:n-1) :: y
\end{lstlisting}
\normalsize
Or C:
\tiny
\lstset{language=C,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
void magicfilter(const int32_t n, const int32_t ndat, const double * x, double * y){
  const int32_t lowfil = -8;
  const int32_t upfil = 7;
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Sample Code: Constructs and Arrays}
The following declaration:
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  unroll = 5
  pr For(j,1,ndat-(unroll-1), unroll) {
  #.....
    pr tt2 === tt2 + x[k,j+1]*fil[l]
  #.....
  }
\end{lstlisting}
\normalsize 
Outputs Fortran:
\tiny
\lstset{language=Fortran,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  do j=1, ndat-4, 5
    !......
    tt2=tt2+x(k,j+1)*fil(l)
    !......
  enddo
\end{lstlisting}
\normalsize
Or C:
\tiny
\lstset{language=C,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  for(j=1; j<=ndat-4; j+=5){
  /*...........*/
    tt2=tt2+x[k-0+(j+1-1)*(n-1-0+1)]*fil[l-lowfil];
  /*...........*/
  }
\end{lstlisting}
\end{frame}

>>>>

\begin{frame}[fragile]
\frametitle{Sample Code: Procedure Declaration}
The following declaration:
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
p = Procedure("magic_filter", [n,ndat,x,y], [lowfil,upfil])
opn p
\end{lstlisting}
\normalsize 
Outputs Fortran:
\tiny
\lstset{language=Fortran,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
subroutine magicfilter(n, ndat, x, y)
  integer(kind=4), parameter :: lowfil = -8
  integer(kind=4), parameter :: upfil = 7
  integer(kind=4), intent(in) :: n
  integer(kind=4), intent(in) :: ndat
  real(kind=8), intent(in), dimension(0:n-1, ndat) :: x
  real(kind=8), intent(out), dimension(ndat, 0:n-1) :: y
\end{lstlisting}
\normalsize
Or C:
\tiny
\lstset{language=C,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
void magicfilter(const int32_t n, const int32_t ndat, const double * x, double * y){
  const int32_t lowfil = -8;
  const int32_t upfil = 7;
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Sample Code: Constructs and Arrays}
The following declaration:
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  unroll = 5
  pr For(j,1,ndat-(unroll-1), step: unroll) {
  #.....
    pr tt2 === tt2 + x[k,j+1]*fil[l]
  #.....
  }
\end{lstlisting}
\normalsize 
Outputs Fortran:
\tiny
\lstset{language=Fortran,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  do j=1, ndat-4, 5
    !......
    tt2=tt2+x(k,j+1)*fil(l)
    !......
  enddo
\end{lstlisting}
\normalsize
Or C:
\tiny
\lstset{language=C,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  for(j=1; j<=ndat-4; j+=5){
  /*...........*/
    tt2=tt2+x[k-0+(j+1-1)*(n-1-0+1)]*fil[l-lowfil];
  /*...........*/
  }
\end{lstlisting}
\end{frame}
